Artistic Curve Steganography Carried by Musical Audio

### 2022-11-15 writeup/paper.tex
Adding 2D examples

\subsubsection{Viterbi Re-Parameterization}
Beyond shifting and scaling the targets coordinates vertically, we may also need to re-parameterize them in time, since, in general, the SWS-STFT sequence will not have the same number of samples as the target $T$.  Let $M$ be the number of samples of the SW-STFT and $N$ be the number of samples of the target, and assume that $N > M$.

@@

@@

As a rule of thumb, we find that having a target curve with about 1.5-2x as many samples as there are SWS-STFT frames gives enough wiggle room for the Viterbi algorithm.  Therefore, in our experiments in Section~\ref{sec:experiments}, we will generate TSP and Hamiltonian sequences with 2000 samples for our 1200-1300 SWS-STFT frames

>>>>

\subsubsection{Viterbi Re-Parameterization}
Beyond shifting and scaling the targets coordinates vertically, we may also need to re-parameterize them in time, since, in general, the SWS-STFT sequence will not have the same number of samples as the target $T$.  Let $M$ be the number of samples of the SW-STFT and $N$ be the number of samples of the target, and assume that $N > M$ (we can always resample our target curves to make this true).

@@

\algrenewcommand\algorithmicindent{0.8em}%
\begin{algorithm}
  \caption{Stipple Tunes Algorithm}

  \begin{algorithmic}[1]
    \Procedure{StippleTune}{$Z$, $x$, na, win, tw} \Comment{$Z$ is stipple, $x$ is audio samples, {\em na} is number of discrete angle states, {\em win} is number of samples between angle states, and {\em tw} is amount by which angle can jump each step}
    \State $N \gets \text{len}(x)$ \Comment{Number of audio samples}
    \State $Y \gets x + ix$
    \State Setup a KDTree {\em tree} for fast NN queries on $Z$
    \State $M \gets \text{ceil}(N / \text{win})$
    \State $C[i, 0] \gets 0, C[i, j > 1] \gets \infty$ \Comment{$na \times M$ Cumulative cost matrix}
    \State $I[i, j] \gets 0$ \Comment{$na \times M$ backpointers to best preceding state}
    \For{$t = 2:M$}
        \For{$j = 1:na$}
            \State $\theta_j \gets 2 \pi j / \text{na}$
            \For{$k = j-\text{tw}:j-1 \mod \text{na}$}
                \State $\theta_k \gets 2 \pi k / \text{na}$ \label{lst:line:interpolate}
                \State Let $\theta_{\ell} \gets \theta_j + (\theta_k-\theta_j)/\text{win}$ 
                \State $d \gets \sum_{\ell = 1}^{\text{win}} \text{tree.query}(Y[\text{win}*t + \ell] e^{i \theta_{\ell}})$ \Comment{Sum nearest neighbors of all points}
                \If{$C[k, t-1] + d < C[j, t]$}
                    \State $C[j, t] \gets C[k, t-1] + d$ 
                    \State $I[j, t] \gets k$  \Comment{Remember optimal transition}
                \EndIf
            \EndFor
        \EndFor
    \EndFor \\
    \State Backtrace $I$ to obtain the optimal sequence of angle states
    \State Linearly interpolate between each angle state (line~\ref{lst:line:interpolate}) to compute $\theta[k], k = 1 \text{ to } N$ 
    \State Let $X_k$ be the nearest neighbor in $Z$ to $Y_k e^{i \theta[k]}$, using {\em tree} to speed up queries \\
    \Return $X$
    \EndProcedure
  \end{algorithmic}
  \label{alg:stippletunes}
\end{algorithm}

@@

As a rule of thumb, we find that having a target curve with about 1.5-2x as many samples as there are SWS-STFT frames gives enough wiggle room for the Viterbi algorithm.  In our experiments in Section~\ref{sec:experiments}, we will generate TSP and Hamiltonian sequences with 2000 samples for our 1200-1300 SWS-STFT frames
